Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 overall.tex
Address Jack's issue #11

Figure~\ref{fig:backfill-utilization} (gray bars) shows the number of Titan
core-hours used by ATLAS during the experiment time window. ATLAS consumed a
total of 73.8M Titan core-hours, for an average of $\approx$7M Titan core-hours
a month, with a minimum of 3.3M Titan core-hours in April 2016 and a maximum
14.8M Titan core-hours in February 2017.

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/backfill_consumption.pdf}
    \caption{Gray bars: Number of unused cores of Titan's backfill availability;
    green bars: Number of cores of backfill availability used by ATLAS via PanDA
    Brokers on Titan; red labels: Efficiency of PanDA Brokers on Titan defined
    as percentage of backfill availability used every month of the experiment
    window.}
\label{fig:backfill-utilization}
\end{figure}

>>>>

Figure~\ref{fig:backfill-utilization} (gray bars) shows the number of
core-hours used by ATLAS during the experiment time window. ATLAS consumed a
total of 73.8M core-hours, for an average of $\approx$7M core-hours a month,
with a minimum of 3.3M core-hours in April 2016 and a maximum 14.8M core-hours
in February 2017.

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/backfill_consumption.pdf}
    \caption{Gray bars: Number of unused cores of Titan's backfill availability;
    blue bars: Number of cores of Titan's backfill availability used by ATLAS
    via PanDA Brokers; red labels: Efficiency of PanDA Brokers defined as
    percentage of Titan's backfill availability used by ATLAS.}
\label{fig:backfill-utilization}
\end{figure}
